---
title: "simpleRegress"
author: "Estrella Aguilar"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
ourweight <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(ourweight)
summary.lm(ourweight)
```

so far the order is that neck is better weight.  
  
weight:RSE:5.432, ARs:0.7423
  
neck:RSE:5.376 ARs: 0.7476

```{r}
ourchest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(ourchest)
summary.lm(ourchest)
```

The order from the worst to best is weight, neck, chest.
  
weight:RSE:5.432, ARs:0.7423
  
neck:RSE:5.376 ARs: 0.7476
  
chest: RSE:4.939 ARs: 0.7869


```{r}
ourheadwth <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(ourheadwth)
summary.lm(ourheadwth)
```


the order from worst to best would be headwth,weight,neck,chest
  
headwth: RSE: 7.32    ARs: 0.5321
  
weight:RSE:5.432, ARs:0.7423
  
neck:RSE:5.376 ARs: 0.7476
  
chest: RSE:4.939 ARs: 0.7869

```{r}
ourheadlen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(ourheadlen)
summary.lm(ourheadlen)
```
the order from worst to best would be headwth,weight,neck,chest,headlen.

headwth: RSE: 7.32    ARs: 0.5321
  
weight:RSE:5.432, ARs:0.7423
  
neck:RSE:5.376 ARs: 0.7476
  
chest: RSE:4.939 ARs: 0.7869
  
headlen: RSE: 4.235  ARs: 0.8434



